Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression

### 2024-11-29 paper/paper.qmd
Data Sheet updated， LLM claimed， Sketches updated
Data Sheet updated，
 LLM claimed，
Sketches updated

## Overview
The dataset used in this study comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority[@greenp] and collected by Bike Share Toronto[@bike]. It records every bike-sharing usage in the Toronto area from 2015 to September 30, 2024, with a total of 28,017,329 records. The variables included in the data differ across years, but they all contain the following variables: Trip ID, Trip Duration, Trip Start Station ID, Trip Start Time, Trip Start Station Location, Trip End Station ID, Trip End Time, Trip End Station Location, Bike ID, and User Type.

>>>>

## Overview
The dataset used in this study is named "Bike Share Toronto Ridership Data" [@bikesharedata]. It comes from opendatatoronto [@opendata], uploaded by Toronto Parking Authority[@greenp] and collected by Bike Share Toronto[@bike]. It records every bike-sharing usage in the Toronto area from 2015 to September 30, 2024, with a total of 28,017,329 records. The variables included in the data differ across years, but they all contain the following variables: Trip ID, Trip Duration, Trip Start Station ID, Trip Start Time, Trip Start Station Location, Trip End Station ID, Trip End Time, Trip End Station Location, Bike ID, and User Type.
